### 2024-06-17 basic-statistics.qmd
20240616 - typo
20240616 - grammar
20240616 - emphasis

There are various indices of each.
Indices to describe the center of a variable's data include:

@@

Indices to describe the center of a variable's data include:

@@

Indices to describe the shape of a variable's data include:

@@

The alternative hypothesis ($H_1$) is the researcher's hypothesis that they want to evaluate.
An alternative hypothesis ($H_1$) might directional or non-directional.

@@

A Statistical Decision Tree For Choosing an Appropriate Statistical Procedure. Adapted from: <https://commons.wikimedia.org/wiki/File:InferentialStatisticalDecisionMakingTrees.pdf>. The original source is: Corston, R., & Colman, A. M. (2000). *A crash course in SPSS for Windows*. Wiley-Blackwell. Changes were made to the original, including the addition of several statistical tests.
:::

>>>>

There are various indices of each.
Indices to describe the *center* of a variable's data include:

@@

Indices to describe the *variability* of a variable's data include:

@@

Indices to describe the *shape* of a variable's data include:

@@

The alternative hypothesis ($H_1$) is the researcher's hypothesis that they want to evaluate.
An alternative hypothesis ($H_1$) might be directional (i.e., one-sided) or non-directional (i.e., two-sided).

@@

A Statistical Decision Tree For Choosing an Appropriate Statistical Procedure. Adapted from: <https://commons.wikimedia.org/wiki/File:InferentialStatisticalDecisionMakingTrees.pdf>. The original source is: Corston, R. & Colman, A. M. (2000). *A crash course in SPSS for Windows*. Wiley-Blackwell. Changes were made to the original, including the addition of several statistical tests.
:::
